\begin{center}
    \small\setlength{\parskip}{\baselineskip}
    Star Trek: Fate\\
    Copyright \copyright\ 2013--\the\year\ Chris Bouchard

    {\Huge\ccbync}

    This work is licensed under a Creative Commons Attribution\-/NonCommercial
    license. To view a copy of this license, visit
    \url{http://creativecommons.org/licenses/by-nc/4.0/}.

    First published in 2013 by Chris Bouchard.

    Fate\texttrademark\ is a trademark of Evil Hat Productions, LLC. The
    Powered by Fate logo is \copyright\ Evil Hat Productions, LLC and is used
    with permission.

    This work is based on Fate Core System and Fate Accelerated Edition (found
    at \url{http://www.faterpg.com/}), products of Evil Hat Productions, LLC,
    developed, authored, and edited by Leonard Balsera, Brian Engard, Jeremy
    Keller, Ryan Macklin, Mike Olson, Clark Valentine, Amanda Valentine, Fred
    Hicks, and Rob Donoghue, and licensed for our use under the Creative
    Commons Attribution 3.0 Unported license
    (\url{http://creativecommons.org/licenses/by/3.0/}).

    This work is also based on the Fate System Toolkit (found at
    \url{http://www.faterpg.com/}), a product of Evil Hat Productions, LLC,
    developed, authored, and edited by Robert Donoghue, Brian Engard, Brennan
    Taylor, Mike Olson, Mark Diaz Truman, Fred Hicks, and Matthew Gandy, and
    licensed for our use under the Creative Commons Attribution 3.0 Unported
    license.

    Star Trek, Star Trek: The Animated Series, Star Trek: The Next Generation,
    Star Trek: Deep Space Nine, Star Trek: Voyager, and Star Trek: Enterprise
    are all registered trademarks of CBS Corporation. We offer no suggestion
    that this work is ``official'' or produced or sanctioned by the owner of
    the aforementioned trademarks. We make no claim to own Star Trek or any of
    the names related to it.

    This work is based on material found on Memory Alpha (found at
    \url{http://en.memory-alpha.org/}) and licensed for our use under the
    Creative Commons Attribution\-/NonCommercial 2.5 Generic license
    (\url{http://creativecommons.org/licenses/by-nc/2.5/}).
\end{center}

